% TeX Format

% version
\def\content{VIMPERATOR}
\def\versionnumber{1.3}  % Version of this reference card

\def\version{v\versionnumber\ \month\ \year}

% include definitions
\input mydefs.sty

% Card content
% Header
%\hrule\vskip 3pt

\title{\uppercase{\content\ quick reference card}}

\shortintro

\section{Page \& Tab Movements}{Short introduction to Vimperator can be found
at:\\http://www.linuxjournal.com/article/10636}
\subsection{Page Movements}{Move commands work as you would expect them to do
from VIM. See {\tt :h motion} for detailed documentation.}
\cmdS{hjkl}	{move left/down/up/right}
\cmdS{gg~G}	{move to top/bottom of page}
\cmdS{\ctrl f~\ctrl d~\ctrl j}	{move screen/page/line down}
\cmdS{\ctrl b~\ctrl u~\ctrl k}	{move screen/page/line up}
\cmdS{/~?}	{search in page, backwards}
\cmdS{n~N}	{jump to next/previous search result}

% subsect %% page_movements (end)

\subsection{Tab \& Buffer Movements}{}
\cmdS{b$n$}	{switch to open buffer $n$ from list}
\cmdS{gt\\or\ctrl n}	{go to next tab}
\cmdS{gT\\or\ctrl p}	{go to previous tab}
\cmdS{g0~g\$}	{go to first/last tab}
% \cmdS{g@}	{switch to first app tab}
\cmdS{gh~gH}	{open own defined homepage, new tab}
\cmdS{gu~gU}	{move up one path/all to root}
\cmdExmpl{moves up to http\ldots or.org/system}	{gu http://www.vimperator.org/system/app/}
\cmdS{go\lbrack aA-zZ0-9\rbrack}	{jump to previously marked web page}

% subsect %%  (end)

\section{General Keybinds}{see: {\tt :h :open}}
\cmdS{o~t}	{open url in current/new tab}
\cmdS{d~u}	{close current/undo last tab}
\cmdS{y~Y}	{copy current url/selection to clipboard}
\cmdS{p~P}	{paste from clipboard, in a new tab}
\cmdS{t~T}	{open new tab, with current url}
\cmdS{H~L}	{go to previous/next page in history}
\cmdS{m~M}	{Set local/global mark at cursor/url}
\cmdS{a~A}	{add/toggle bookmark}
\cmdS{i~I}	{ignore any/specific {\tt vimperator} keybind}
\cmdS{\lbracket\lbracket~\rbracket\rbracket}	{switch to previous/next page on multipage websites}
\cmdS{+~-}	{zoom in/out by 25 \% on page in focus}
\cmdS{$n$zz}	{zoom page to $n$\% (100 if $n$ is omitted)}
\cmdS{ZZ~ZQ}	{exit browser, clear history before}

\section{Exe commands}{Works with tab completion}
\cmdS{:addo\grey{ns}}	{show addons in current window}
\cmdL{:bmark~:delb\grey{marks} $url$}	{add/delete bookmark}
\cmdS{:em\grey{enu} \tab}	{command-line access to Firefox menubar}
\cmdS{:hist\grey{ory}}	{pull up recent 10 online \& local pages}
\cmdS{:pc\grey{lose}}	{close preview window, eg. history}
\cmdS{:pref\grey{erences}}	{show preferences}
\cmdS{:res\grey{tart}}	{restart Firefox immediately}
\cmdS{:tabo\grey{nly}}	{close all other tabs}
\cmdS{:sav\grey{eas}}	{save current web page to disk.}

\section{Panorama Mode (Tab Group Management)}{Start tabgroup management with {\tt :tabgroup subcom}}
Some subcommands \ldots \\
\cmdOper{add}	{create new {\tt tab group}}
\cmdOper{list}	{list current {\tt tab groups}}
\cmdOper{rm}	{remove group with {\tt group}name}
\cmdOper{pull-\or pushtab}	{pull tab from\or move to {\tt group}}
\cmdOper{switch}	{switch to {\tt group}name}



% subsect %%  (end)

\section{Hint-Modes}{Hints are the way in which Vimperator allows you to follow links on a page. By
providing each link with a suitable hint, you can access them via a set of hotkeys. }
\subsection{QuickHint Mode ($f$)}{Simulates mouseselection with labeled
links on web page. To run new tab in background change to uppercase $F$.}
\subsection{ExtendedHint Mode ( ; )}{This mode is useful for
performing operations on hinted elements other than the default
left mouse click. If you want to yank the location of hint 24, press ;y to start this hint
mode. Then press 24 to copy the hint location.}
\cmdL{:h extended-hints}	{list all extended mode commands}
here are a few \ldots\\
\cmdS{;~}	{imitates mouse-hovering a link object}
\cmdS{s~S}	{save link/object}
\cmdS{i~I}	{open media object (in new tab)}
\cmdS{y~Y}	{copy URL/label description to clipboard}

% Footer
\copyrightnotice
%


% Ending
\vfil
\supereject
\if L\lr \else\null\vfill\eject\fi
\if L\lr \else\null\vfill\eject\fi
\bye

% EOF
